---
title: "Germinacion"
format: html
editor: "Edwin"
---
# cargar lybrari
```{r}
source("https://inkaverse.com/setup.r")
li
```


# Importar datos
```{r}
url <- "https://docs.google.com/spreadsheets/d/1Eg67TqQINnAfa29ncqlPCAN7umUbyrkBbNOjd1us85Q/edit?gid=1454035531#gid=1454035531"

gs <- as_sheets_id(url)

fb <- range_read(gs
                 , sheet = "fb") %>% 
  mutate(across(factor1,  ~as.factor(.))) %>% 
  dplyr::select(!c(ger_7, ger_8, ger_9, ger_10)) %>% 
  as.data.frame()
str(fb)
```


```{r}
gsm <- ger_summary(SeedN = "seed"
                   , evalName = "ger_"
                   , data = fb
                   )
gsm %>% kable()
##Tiempo medio de germinacion```
```
## Germination Percentage (GRP)

```{r}
# analysis of variance

av <- aov(mgt ~ block + factor1, data = gsm)
anova(av)

# mean comparison test

mc_grp <- ger_testcomp(aov = av
                       , comp = c("factor1")
                       , type = "snk"
                       )

# data result

mc_grp$table %>% 
   kable(caption = "Mean germinacion time comparison")

# date result

plot <- mc_grp$table %>% 
   plot_smr (data = .
       , type = "bar"
       , x = "factor1"
       , y = "mgt"
       # , ylimits = c(0, 3, 0.5)
       , error = "ste"
       , sig = "sig"
       # , color = F
       )
plot
```
#Germinacion en el tiempo
```{r}
git <- ger_intime(Factor = "factor1"
                  , SeedN = "seed"
                  , evalName = "ger_"
                  , method = "percentage"
                  , data = fb
                  )

# data result

git %>% 
   kable(caption = "Cumulative germination by nacl factor")

plot <- git %>% 
   fplot(data = .
        , type = "line"
        , x = "evaluation"
        , y = "mean"
        , group = "factor1
        "
        , ylimits = c(0, 110, 10)
        , ylab = "Germination ('%')"
        , xlab = "Day"
        , color = T
        , error = "ste"
        )
plot
```

